Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-30 demystify.tex
updates

\begin{center}
  \includegraphics[scale=0.4]{files/c2.png}
\end{center}

@@

In your SOP, focus on research motivation and convince us that you can achieve it through your experience, e.g., published papers. You should also back up your claims with concrete evidence. For example, if you say you have experience with teaching, then show what you did, e.g., undergrad TA or mentoring someone.  If you say you work on a project, then show some results, e.g., paper submitted (or even rejected), achieved X\% performance improvement over ... Also, do not use more than two pages (references can be on the third page). Many SOP samples are \href{https://cs-sop.org/}{available here}.

@@

@@

@@

Most of what is written in this document applies to both domestic\footnote{For simplicity domestic means you did your undergrad (or MS) at a US university.} and international students.  However, there are some differences and benefits that domestic students should be aware of.

@@

\paragraph{Research Experiences \autoref{sec:research-opportunities}} You might have many opportunities to do research as an undergraduates, e.g., through REUs and internships at your undergrad university.  Highlight such experiences in your application.

@@

\chapter{Research Opportunities}\label{sec:research-opportunities}
\begin{center}
    \includegraphics[scale=0.5]{files/phd100404s.png}
  \end{center}

@@

@@

@@

>>>>

\begin{center}
  \includegraphics[scale=0.5]{files/c2.png}
\end{center}

@@

In your SOP, focus on research motivation and convince us that you can achieve it through your experience, e.g., published papers. You should also back up your claims with concrete evidence. For example, if you say you have experience with teaching, then show what you did, e.g., undergrad TA or mentoring someone.  If you say you work on a project, then show some results, e.g., paper submitted (or even rejected), achieved certain performance improvement over the state of the art. Also, do not use more than two pages (references can be on the third page). Many SOP samples are \href{https://cs-sop.org/}{available here}.

@@

\epigraph{\vspace{-0.2in} The answer to life's problems aren't at the bottom of a bottle. Heh heh! They're on TV!}{\textsc{The Simpsons}}

@@

\epigraph{\vspace{-0.2in} I didn’t do it. Nobody saw me do it. You can’t prove anything!}{\textsc{The Simpsons}}

@@

\epigraph{\vspace{-0.2in} I’m not a bad guy! I work hard, and I love my kids. So why should I spend half my Sunday hearing about how I’m going to Hell?}{\textsc{The Simpsons}}

Most of what is written in this document applies to both domestic\footnote{For simplicity domestic means you did your undergrad (or MS) at a US university.} and international students.  However, there are some differences and benefits that domestic students should be aware of and can leverage to improve their chances of admission.

@@

\paragraph{Research Experiences \autoref{sec:research-opportunities}} You might have many opportunities to do research as an undergraduate, e.g., through REUs and internships at your undergrad university.  Highlight such experiences in your application.

@@

\chapter{Research Opportunities}\label{sec:research-opportunities}

\epigraph{\vspace{-0.2in} Kids, you tried your best and you failed miserably. The lesson is: never try.}{\textsc{The Simpsons}}

\begin{center}
    \includegraphics[scale=0.5]{files/phd100404s.png}
  \end{center}

@@

\epigraph{\vspace{-0.2in} Ay caramba!}{\textsc{The Simpsons}}

@@

\epigraph{\vspace{-0.2in} The whole damn system is wrong!}{\textsc{The Simpsons}}

@@

Also thanks to NSF its flexibility and allows faculty to be creative in research and education, which allows me to have time to write this document.
